---
title: "P8105_HW_05"
author: "James Ng"
date: "11/7/2019"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Problem 1

* Problem Setup
```{r iris}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

* function code for filling in missing values
```{r function}
fill_in = function(x) {
  
  if (!is.numeric(x)) {
    replace_na(x,"virginica")
  } else if (is.numeric(x)) {
    replace_na(x,mean(x,na.rm=TRUE))
  }
  
}
```

* map function to fill in the missing values
```{r iris full}
iris_full=map(iris_with_missing,fill_in)
```

## Problem 2

```{r function_2}
study_tidy = function(arm) {
  
  x = read_csv(arm)
  
  x %>% 
    janitor::clean_names() %>% 
    pivot_longer(
      week_1:week_8,
      names_to = "week",
      values_to = "observation"
      )
  
}
```

```{r one tibble,message=FALSE}
study = 
  tibble(
    subject = str_c("./data/",list.files("./data"))
  ) %>% 
  mutate(
    output = map(subject, study_tidy),
    subject = str_remove(subject,"./data/"),
    subject = str_remove(subject,".csv"),
  ) %>% 
  unnest(output) %>% 
  #separate(subject,c("group","subject")) %>% 
  mutate(
    week = str_remove(week,"week_"),
    week = as.numeric(week)
  )
```

```{r ,warning=FALSE}
study %>%  
  ggplot(aes(x=week,y=observation,color=subject))+
  geom_line()+
  labs(
    title = "Changes in Observations Over Weeks By Subject")
```

This plot makes it hard to separate the groups to see the trends so I faceted the plot into the two arms.

```{r ,warning=FALSE}
study2=study %>% 
  mutate(
   arm=subject,
  ) %>% 
  separate(arm,"arm",sep = "_")
  
study2 %>%  
  ggplot(aes(x=week,y=observation,color=subject))+
  geom_line()+
  facet_grid(~arm)+
  labs(
    title = "Changes in Observations Over Weeks By Subject and Group")
```

This chart lets us see that the experimental arm's observational data is increasing in value over the weeks whereas the values are mostly constant in the control arm. We do not know what the data describes so we cannot determine if this is a good change or not.

## Problem 3

```{r}
set.seed(1)

sim_regression = function(n=30, beta0 = 2, beta1 = 0) {
  
  sim_data = tibble(
    x = rnorm(n, mean = 1, sd = 1),
    y = beta0 + beta1 * x + rnorm(n, 0, 50)
  )
  
  ls_fit = lm(y ~ x, data = sim_data)
  broom::tidy(ls_fit)
  #tibble(
  #  beta0_hat = coef(ls_fit)[1],
  #  beta1_hat = coef(ls_fit)[2]
  #)
}

```

```{r}
output = 
  rerun(1, sim_regression(beta1 = 1)) %>% 
  bind_rows() 
#output %>%   ggplot(aes(x = beta0_hat)) + geom_density()
```


```{r}
sim_results = 
  tibble(
    beta1_val = c(0, 1, 2, 3,4,5,6)
  ) %>% 
  mutate(
    output_list = map(.x = beta1_val, ~ rerun(10000, sim_regression(beta1 = .x))),
    output_df = map(output_list, bind_rows)
  ) %>% 
  select(-output_list) %>% 
  unnest(output_df)
```

